Notes on Big MRA

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save5.tex
updates on section 2

We fix a value $\Delta$ between $1$ and $L-1$. We will compute the second moment:
%
\begin{align}
%
    M_2(\Delta) = 
        \lim_{n \to \infty} \frac{1}{n} \sum_{i=1}^{n-\Delta} Y_i Y_{i+\Delta}.
%
\end{align}

First, if there is no noise, and under the wide spacing assumption, we can break the sum into $J_n$ different sums, one for each copy of $x$ embedded in the signal:
%
\begin{align}
%
    M_2(\Delta) 
        &= \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=a_j}^{b_j-\Delta} Y_i Y_{i+\Delta}
        = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta}
    \nonumber \\
    &= \frac{J_n L}{n} \frac{1}{L} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta}
        \to \gamma \cdot m_2(\Delta),
%
\end{align}
%
where here we have defined $m_2(\Delta)$ as element $\Delta$ of the (circular) autocorrelation of the zero-padded signal $\tilde{x} = [x,0] \in \mathbb{R}^{2L}$.

>>>>

We fix a value $\Delta$ between $0$ and $L-1$. We will compute the second moment:
%
\begin{align}
%
    M_2(\Delta) = 
        \lim_{n \to \infty} \frac{1}{n} \sum_{i=1}^{n-\Delta} Y_i Y_{i+\Delta}.
%
\end{align}

First, if there is no noise, and under the wide spacing assumption, we can break the sum into $J_n$ different sums, one for each copy of $x$ embedded in the signal:
%
\begin{align}
%
    M_2(\Delta) 
        &= \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=a_j}^{b_j-\Delta} Y_i Y_{i+\Delta}
        = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta}
    \nonumber \\
    &= \frac{J_n L}{n} \frac{1}{L} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta}
        \to \gamma \cdot R_2(\Delta),
%
\end{align}
%
where here we have defined $R_2(\Delta)$ as element $\Delta$ of the (circular) autocorrelation of the zero-padded signal $\tilde{x} = [x,0] \in \mathbb{R}^{2L}$, and $\gamma = \lim_{n\to\infty} J_n L / n$ is the fraction of the observations containing the signal.
%

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save6.tex
updates on section 2

First, if there is no noise, and under the wide spacing assumption, we can break the sum into $J_n$ different sums, one for each copy of $x$ embedded in the signal:
%
\begin{align}
%
    M_2(\Delta) 
        &= \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=a_j}^{b_j-\Delta} Y_i Y_{i+\Delta}
        = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta}
    \nonumber \\
    &= \frac{J_n L}{n} \frac{1}{L} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta}
        \to \gamma \cdot R_2(\Delta),
%
\end{align}
%
where here we have defined $R_2(\Delta)$ as element $\Delta$ of the (circular) autocorrelation of the zero-padded signal $\tilde{x} = [x,0] \in \mathbb{R}^{2L}$, and $\gamma = \lim_{n\to\infty} J_n L / n$ is the fraction of the observations containing the signal.
%

>>>>

First, if there is no noise, and under the wide spacing assumption, we can break the sum into $J_n$ different sums, one for each copy of $x$ embedded in the signal:
%
\begin{align}
%
    M_2(\Delta) 
        &= \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=a_j}^{b_j-\Delta} Y_i Y_{i+\Delta}
        = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta}
    \nonumber \\
    &= \frac{J_n L}{n} \frac{1}{L} \sum_{i=1}^{L-\Delta} x_i x_{i+\Delta}
        \to \gamma \cdot R_2(\Delta),
%
\end{align}
%
where here we have defined $R_2(\Delta)$ as element $\Delta$ of the autocorrelation of $x$, and $\gamma = \lim_{n\to\infty} J_n L / n$ is the fraction of the observations containing the signal.
%

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save8.tex
updates on section 2

\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}

@@

We will assume that the first and last copies of $x$ is at least $L$ places removed from the boundaries of the interval $[1,n + L]$ (if not we can just zero-pad the interval). We will also denote by $I_1,\dots,I_J$ the $J$ subintervals containing the signal; and take $I_j = [a_j,b_j]$. When we take the limit $n \to \infty$, we'll let $J = J_n$ grow with $n$, as is natural. We will see that we require $J_n = \Omega(n)$ in order for the limits to not vanish (and obviously $J_n = O(n)$ too).

@@

This part is now easy. Denote by $\XX = x \ast g$, so $Y = \XX + \ep$. Then the second moment of the signal plus noise is:
%
\begin{align}
%
    M_2(\Delta,Y) = M_2(\Delta,\XX) + M_2(\Delta,\ep) 
        + \frac{1}{n}\sum_{i=1}^{n-\Delta} \XX_i \ep_{i+\Delta}
        + \frac{1}{n}\sum_{i=1}^{n-\Delta} \XX_{i+\Delta} \ep_i.
%
\end{align}
%
The law of large numbers says the cross terms vanish as $n \to \infty$. So the limit is simply:
%
\begin{align}
%
    M_2(\Delta,Y) = 
    \begin{cases}
        R_2(\Delta), &\text{ if } \Delta > 0; \\
        R_2(\Delta) + \sigma^2, &\text{ if } \Delta = 0.
    \end{cases}
%
\end{align}

\section{Third moments}

The same idea lets us compute the third moments. We fix two indices $\Delta_1 < \Delta_2$, and define:
%
\begin{align}
%
    M_3(\Delta_1,\Delta_2) = \sum_{i=1}^{n-\Delta_2} Y_i Y_{i+\Delta_1} Y_{i+\Delta_2}.
%
\end{align}

\section{Pure noise, no signal}

Again, the idea is to break up the big average into a fixed number of averages of $\approx n$ independent terms.

>>>>

\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}

@@

We will assume that the first and last copies of $x$ is at least $L$ places removed from the boundaries of the interval $[1,n + L]$ (if not we can just zero-pad the interval). We will also denote by $I_1,\dots,I_J$ the $J$ subintervals containing the signal; and take $I_j = [a_j,b_j]$. When we take the limit $n \to \infty$, we'll let $J = J_n$ grow with $n$, as is natural. We will see that we require $J_n = \Omega(n)$ in order for the limits to not vanish.

@@

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save.tex
updates on section 2

\documentclass{article}
\usepackage{amsthm,amsmath,amssymb}
\usepackage{url} 
\usepackage[authoryear]{natbib}
%%%\usepackage{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{framed}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%%%\usepackage{custom_tex}
\usepackage{grffile}
\usepackage{multirow}
\usepackage{xcolor}
%\usepackage{setspace}
\usepackage{comment}
\usepackage{xr}
%\externaldocument{sharp_PCA_AoS_supp}

@@

%
%
%
%
\begin{document}
\title{Notes on big MRA}
\author{William Leeb}
\date{}
\maketitle

@@

Similarly, if $\Delta_1 = 0$, then there is a surviving cross-term which converges to $\gamma \cdot \sigma^2 \cdot \bar{x}$ as well. So in summary,
%
\begin{align}
%
    M_3(\Delta_1,\Delta_2,Y) = 
    \begin{cases}
        \gamma \cdot R_3(\Delta_1,\Delta_2), &\text{ if } 0 < \Delta_1 < \Delta_2; \\
        \gamma \cdot R_3(\Delta_1,\Delta_2) + \gamma \cdot \sigma^2 \cdot \bar{x},
                        &\text{ if } \Delta_1 = 0 \text{ or } \Delta_1 = \Delta_2.
    \end{cases}
%
\end{align}

@@

But finding this minimum is hard, since the sum is over all ${n}\choose{J}$ possible values of $G$; if $J \sim n$, as we expect is necessary to have any chance of recovery (this was suggested by the moments method), the number of terms will grow exponentially with $n$.

>>>>

\documentclass{article}
\usepackage{amsthm,amsmath,amssymb}
\usepackage{url} 
\usepackage[authoryear]{natbib}
%%%\usepackage{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{framed}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%%%\usepackage{custom_tex}
\usepackage{grffile}
\usepackage{multirow}
\usepackage{xcolor}
%\usepackage{setspace}
\usepackage{comment}
\usepackage{xr}

@@

%
%
%
%

\begin{document}
\title{Notes on Big MRA}
\author{William Leeb}
\date{}
\maketitle

@@

Similarly, if $\Delta_1 = 0$, then there is a surviving cross-term which converges to $\gamma \cdot \sigma^2 \cdot \bar{x}$ as well. So in summary, for all $0 \le \Delta_1 \le \Delta_2 \le L-1$, we have:
%
\begin{align}
%
    M_3(\Delta_1,\Delta_2,Y) = 
    \begin{cases}
        \gamma \cdot R_3(\Delta_1,\Delta_2), &\text{ if } 0 < \Delta_1 < \Delta_2; \\
        \gamma \cdot R_3(\Delta_1,\Delta_2) + \gamma \cdot \sigma^2 \cdot \bar{x},
                &\text{ if } \Delta_2 > \Delta_1 = 0 \text{ or } \Delta_1 = \Delta_2 > 0; \\
        \gamma \cdot R_3(0,0) + 3\cdot \gamma \cdot \sigma^2 \cdot \bar{x}
                &\text{ if } \Delta_1 = \Delta2 = 0.
    \end{cases}
%
\end{align}

@@

But finding this minimum is hard, since the sum is over all ${n}\choose{J}$ possible values of $G$; if $J \sim n$, as we expect is necessary to have any chance of recovery (this was suggested by the moments method), the number of terms will grow super-exponentially with $n$.

\section{Estimating $J$, the number of copies of $x$}

Using the moments calculation, we can estimate the number of copies of $x$ embedded in $Y$, which we call $J$. This permits us to then estimate the unscaled moments of $x$, which in turn lets us fit $x$ to its moments.

From the first moment we estimate $(J / n) (\mathbf{1}^\top x)$, while from the second moment we estimate $(J/n) (\mathbf{1}^\top x)^2$. We can then estimate $J$ via
%
\begin{align}
%
    J = n \cdot \frac{(J / n)^2 (\mathbf{1}^\top x)^2}{(J/n) (\mathbf{1}^\top x)^2}.
%
\end{align}
%

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save2.tex
updates on section 2

If $\Delta_1 = \Delta_2 = \Delta$, there is a surviving cross-term, namely:
%
\begin{align}
%
    \frac{1}{n} \sum_{i=1}^{n-\Delta} \XX_i N_{i+\Delta}^2
    = \frac{1}{(n/L)} \sum_{j=1}^{J_n} \frac{1}{L} \sum_{i=a_j}^{b_j} \XX_i N_{i+\Delta}^2.
%
\end{align}
%
Each of $S_j \equiv \frac{1}{L} \sum_{i=a_j}^{b_j} \XX_i N_{i+\Delta}^2 \sim \frac{1}{L} \sum_{i=1}^{L} x_i \ep_i^2$, where $\ep_i \sim N(0,\sigma^2)$; and they are independent random variables with mean $\E[S_j] = \sigma^2 \cdot \bar{x}$. So by the law of large numbers,
%
\begin{align}
%
    \frac{1}{(n/L)} \sum_{j=1}^{J_n} \frac{1}{L} \sum_{i=a_j}^{b_j} \XX_i N_{i+\Delta}^2
    \to \gamma \cdot \sigma^2 \cdot \bar{x}.
%
\end{align}

Similarly, if $\Delta_1 = 0$, then there is a surviving cross-term which converges to $\gamma \cdot \sigma^2 \cdot \bar{x}$ as well. So in summary, for all $0 \le \Delta_1 \le \Delta_2 \le L-1$, we have:
%
\begin{align}
%
    M_3(\Delta_1,\Delta_2,Y) = 
    \begin{cases}
        \gamma \cdot R_3(\Delta_1,\Delta_2), &\text{ if } 0 < \Delta_1 < \Delta_2; \\
        \gamma \cdot R_3(\Delta_1,\Delta_2) + \gamma \cdot \sigma^2 \cdot \bar{x},
                &\text{ if } \Delta_2 > \Delta_1 = 0 \text{ or } \Delta_1 = \Delta_2 > 0; \\
        \gamma \cdot R_3(0,0) + 3\cdot \gamma \cdot \sigma^2 \cdot \bar{x}
                &\text{ if } \Delta_1 = \Delta_2 = 0.
    \end{cases}
%
\end{align}

>>>>

If $\Delta_1 = \Delta_2 = \Delta > 0$, there is a surviving cross-term, namely:
%
\begin{align}
%
    \frac{1}{n} \sum_{i=1}^{n-\Delta} \XX_i N_{i+\Delta}^2
    = \frac{1}{(n/L)} \sum_{j=1}^{J_n} \frac{1}{L} \sum_{i=a_j}^{b_j} \XX_i N_{i+\Delta}^2.
%
\end{align}
%
Each of $S_j \equiv \frac{1}{L} \sum_{i=a_j}^{b_j} \XX_i N_{i+\Delta}^2 \sim \frac{1}{L} \sum_{i=1}^{L} x_i \ep_i^2$, where $\ep_i \sim N(0,\sigma^2)$; and they are independent random variables with mean $\E[S_j] = \sigma^2 \cdot \bar{x}$. So by the law of large numbers,
%
\begin{align}
%
    \frac{1}{(n/L)} \sum_{j=1}^{J_n} \frac{1}{L} \sum_{i=a_j}^{b_j} \XX_i N_{i+\Delta}^2
    \to \gamma \cdot \sigma^2 \cdot \bar{x}.
%
\end{align}

Similarly, if $\Delta_2 > \Delta_1 = 0$, then there is a surviving cross-term which converges to $\gamma \cdot \sigma^2 \cdot \bar{x}$ as well. Finally, if $\Delta_1 = \Delta_2 = 0$, then the cross-term converges to $3 \cdot \gamma  \cdot \sigma^2 \cdot \bar{x}$. So in summary, for all $0 \le \Delta_1 \le \Delta_2 \le L-1$, we have:
%
\begin{align}
%
    M_3(\Delta_1,\Delta_2,Y) = 
    \begin{cases}
        \gamma \cdot R_3(\Delta_1,\Delta_2), &\text{ if } 0 < \Delta_1 < \Delta_2; \\
        \gamma \cdot R_3(\Delta_1,\Delta_2) + \gamma \cdot \sigma^2 \cdot \bar{x},
                &\text{ if } \Delta_2 > \Delta_1 = 0 \text{ or } \Delta_1 = \Delta_2 > 0; \\
        \gamma \cdot R_3(0,0) + 3\cdot \gamma \cdot \sigma^2 \cdot \bar{x}
                &\text{ if } \Delta_1 = \Delta_2 = 0.
    \end{cases}
%
\end{align}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save3.tex
updates on section 2

\newcommand{\F}{\mathcal{F}}
\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}

@@

\section{Estimating $J$, the number of copies of $x$}

Using the moments calculation, we can estimate the number of copies of $x$ embedded in $Y$, which we call $J$. This permits us to then estimate the unscaled moments of $x$, which in turn lets us fit $x$ to its moments.

From the first moment we estimate $(J / n) (\mathbf{1}^\top x)$, while from the second moment we estimate $(J/n) (\mathbf{1}^\top x)^2$. We can then estimate $J$ via
%
\begin{align}
%
    J = n \cdot \frac{(J / n)^2 (\mathbf{1}^\top x)^2}{(J/n) (\mathbf{1}^\top x)^2}.
%
\end{align}
%

>>>>

\newcommand{\F}{\mathcal{F}}
\newcommand{\LL}{\mathcal{L}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\SUM}{\text{sum}}
\newcommand{\1}{\mathbf{1}}

@@

\section{Estimating $\gamma$, using $\sigma$ and the moments}

We'll suppose we know $\sigma$. Using the moments calculation, we can estimate $\gamma$. This permits us to then estimate the unscaled moments of $x$, which in turn lets us fit $x$ to its moments.

It will be notationally simpler to instead estimate $Q \equiv \gamma \cdot L = J / n$. Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=1,2$. From the first moment we estimate $Q \cdot (\1^\top x)$, and hence also its square:
%
\begin{align}
%
    (Q \cdot (\1^\top x))^2 
    &= Q^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) 
            + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L}x_i x_{i+\Delta} 
        \1_{(\Delta \le L-i)} \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^L \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
        \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta) \right).
%
\end{align}

. From the second while from the second moment we estimate $(J/n) (\mathbf{1}^\top x)^2$. We can then estimate $J$ via
%
\begin{align}
%
    J = n \cdot \frac{(J / n)^2 (\mathbf{1}^\top x)^2}{(J/n) (\mathbf{1}^\top x)^2}.
%
\end{align}
%

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save4.tex
updates on section 2

It will be notationally simpler to instead estimate $Q \equiv \gamma \cdot L = J / n$. Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=1,2$. From the first moment we estimate $Q \cdot (\1^\top x)$, and hence also its square:
%
\begin{align}
%
    (Q \cdot (\1^\top x))^2 
    &= Q^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) 
            + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L}x_i x_{i+\Delta} 
        \1_{(\Delta \le L-i)} \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^L \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
        \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta) \right).
%
\end{align}

. From the second while from the second moment we estimate $(J/n) (\mathbf{1}^\top x)^2$. We can then estimate $J$ via
%
\begin{align}
%
    J = n \cdot \frac{(J / n)^2 (\mathbf{1}^\top x)^2}{(J/n) (\mathbf{1}^\top x)^2}.
%
\end{align}
%

>>>>

It will be notationally simpler to instead estimate $Q \equiv \gamma \cdot L = J / n$. Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=1,2$. From the first moment we estimate $Q \cdot (\1^\top x)$, and hence also its square:
%
\begin{align}
%
    A \equiv (Q \cdot (\1^\top x))^2 
    &= Q^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) 
            + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L}x_i x_{i+\Delta} 
        \1_{(\Delta \le L-i)} \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^L \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
        \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta) \right).
%
\end{align}

On the other hand, from the second moment we can estimate $Q \cdot T_2(\Delta)$ for all $1 \le \Delta \le L-1$, and $Q\cdot T_2(0) + \sigma^2$, and consequently $B \equiv Q \cdot (T_2(0) + 2 \sum_{\Delta=1}^L T_2(\Delta)) + \sigma^2$. Taking the ratio, we obtain the equation:
%
\begin{align}
%
    \frac{1}{Q} + \frac{\sigma^2}{A} = \frac{B}{A}.
%
\end{align}

If we knew $\sigma$, we can solve for $Q$ (and conversely).

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save6.tex
updates on section 2

We'll suppose we know $\sigma$. Using the moments calculation, we can estimate $\gamma$. This permits us to then estimate the unscaled moments of $x$, which in turn lets us fit $x$ to its moments.

It will be notationally simpler to instead estimate $Q \equiv \gamma \cdot L = J / n$. Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=1,2$. From the first moment we estimate $Q \cdot (\1^\top x)$, and hence also its square:
%
\begin{align}
%
    A \equiv (Q \cdot (\1^\top x))^2 
    &= Q^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) 
            + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L-1}x_i x_{i+\Delta} 
        \1_{(\Delta \le L-i)} \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
        \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} T_2(\Delta) \right).
%
\end{align}

@@

(Of course, this only works if $B \ne \sigma^2$, or equivalently if $\1^\top x \ne 0$.)
%
%
%

>>>>

Using the moments calculation, we will derive an equation relating $\gamma$ and $\sigma$. If $\sigma$ were known (and $\1^\top x \ne 0$), this permits us to then estimate the unscaled moments of $x$, which in turn lets us fit $x$ to its moments.

It will be notationally simpler to instead estimate $Q \equiv \gamma \cdot L = J / n$. Also, we'll define the unnormalized moments of $x$ by $T_i = L \cdot R_i$, for $i=2,3$. From the first moment we estimate $Q \cdot (\1^\top x)$, and hence also its square:
%
\begin{align}
%
    A \equiv (Q \cdot (\1^\top x))^2 
    &= Q^2  \left( \sum_{i=1}^L x_i^2 + 2 \sum_{i=1}^L \sum_{j=i+1}^{L} x_i x_j \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) 
            + 2 \sum_{i=1}^{L} \sum_{\Delta=1}^{L-i} x_i x_{i+\Delta}\right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{i=1}^L \sum_{\Delta=1}^{L-1}x_i x_{i+\Delta} 
        \1_{(\Delta \le L-i)} \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} \sum_{i=1}^{L-\Delta}x_i x_{i+\Delta} 
        \right)
        \nonumber \\
    &= Q^2 \left( T_2(0) + 2 \sum_{\Delta=1}^{L-1} T_2(\Delta) \right).
%
\end{align}

@@

(Of course, this only works if $B \ne \sigma^2$, or equivalently if $\1^\top x \ne 0$.)

\section{An equation for $\sigma$}

It turns out that $\nu \equiv \sigma^2$ satisfies a quadratic equation, using third-order moments. The previous section gives the equation:
%
\begin{align}
%
    Q = \frac{A}{B - \nu}.
%
\end{align}

Now we move up to third-order moments. From the first order moments, we can estimate $Q \cdot \1^\top x$; and from the second-order moments we can estimate $Q \cdot \|x\|^2 + \sigma^2$. Taking the product, we have:
%
\begin{align}
%
    C &\equiv (Q \cdot \1^\top x) \cdot (Q \cdot \|x\|^2 + \sigma^2)
        \nonumber \\
    &= Q^2 \left( T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta) \right)
        + \sigma^2 \cdot (Q \cdot \1^\top x).
%
\end{align}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test3_save9.tex
updates on section 2

\section{An equation for $\sigma$}

@@

Now we move up to third-order moments. From the first order moments, we can estimate $Q \cdot \1^\top x$; and from the second-order moments we can estimate $Q \cdot \|x\|^2 + \sigma^2$. Taking the product, we have:
%
\begin{align}
%
    & (Q \cdot \1^\top x) \cdot (Q \cdot \|x\|^2 + \sigma^2)
        \nonumber \\
    &= Q^2 \left( T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta) \right)
        + \sigma^2 \cdot (Q \cdot \1^\top x)
        \nonumber \\
    &= Q^2 \cdot w + \sigma^2 \cdot (Q \cdot \1^\top x),
%
\end{align}
%
where 
%
\begin{math}
%
    w = T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta).
%
\end{math}

From the third-order moments directly, we can estimate $Q\cdot w + (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x)$.

>>>>

\section{A quadratic equation satisfied by $\sigma$}

@@

Now we move up to third-order moments. From the first order moments, we can estimate $Q \cdot \1^\top x$; and from the second-order moments we can estimate $Q \cdot \|x\|^2 + \sigma^2$. Taking the product, we have:
%
\begin{align}
%
    C &\equiv (Q \cdot \1^\top x) \cdot (Q \cdot \|x\|^2 + \sigma^2)
        \nonumber \\
    &= Q^2 \left( T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta) \right)
        + \sigma^2 \cdot (Q \cdot \1^\top x)
        \nonumber \\
    &= Q^2 \cdot w + \sigma^2 \cdot (Q \cdot \1^\top x),
%
\end{align}
%
where 
%
\begin{math}
%
    w = T_3(0,0) + \sum_{\Delta=1}^{L-1}T_3(0,\Delta) 
        + \sum_{\Delta=1}^{L-1}T_3(\Delta,\Delta).
%
\end{math}

From the observed third-order terms themselves, we can estimate:
%
\begin{align}
%
    D \equiv Q\cdot w + (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x).
%
\end{align}

Consequently:
%
\begin{align}
%
    D\cdot Q - Q \cdot (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x)
    = Q^2 \cdot w = C - \sigma^2 \cdot (Q \cdot \1^\top x),
%
\end{align}
%
and therefore
%
\begin{align}
%
    Q = \frac{C - \sigma^2 \cdot (Q \cdot \1^\top x)}
            {D - (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x)}
%
\end{align}

On the other hand, from the first equation relating $Q$ and $\sigma^2$, we see that:
%
\begin{align}
%
    Q = \frac{A}{B - \sigma^2}.
%
\end{align}
%

Putting these together, we have:
%
\begin{align}
%
    \frac{A}{B - \sigma^2}
    = \frac{C - \sigma^2 \cdot (Q \cdot \1^\top x)}
        {D - (2L+1)\cdot\sigma^2\cdot (Q \cdot \1^\top x)}
    = \frac{C - E \cdot \sigma^2}{D - F \cdot \sigma^2},
%
\end{align}
%
where
%
\begin{align}
%
    E = Q \cdot \1^\top x,
%
\end{align}
%
and
%
\begin{align}
%
    F = (2L+1) \cdot Q \cdot \1^\top x.
%
\end{align}

This is a quadratic equation for $\sigma^2$. Unfortunately, it can have two positive solutions, so I'm not sure if it helps...
\end{document}
